---
title: "USDA Farm Income Forecasts"
author: "Lawson Connor"
date: "March 20, 2018"
output: 
 html_document:
    reference_html: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The USDA released its projections for 2019 national farm incomes on March 6^th^. The forecasts say that the USDA expects an increase in farm incomes for the 2019 calendar year.State level estiamtes for 2018 are expected in August of 2018 and estimates for the 2019 year will be released in August of 2020. The national picture does give some insight into the expected performance of the Louisiana farm economy this year. 


### National farm income outlook
The USDA farm income forecasts show that national farm incomes are expected to increase by 8%. 

```{r, include = FALSE}
source("fm_income.R")
```
The USDA released its projections for 2019 national farm incomes on March 6^th^. The forecasts say that the USDA expects an increase in farm incomes for the 2019 calendar year.State level estimates for 2018 are expected in August of 2018 and estimates for the 2019 year will be released in August of 2020. The national picture does give some insight into the expected performance of the Louisiana farm economy this year. 


### National farm income outlook
The USDA farm income forecasts show that national cash incomes are expected to increase by 4.7%. Figure 1 below shows the behavior net farm income for the last few years. 

```{r, include = FALSE}
source("fm_income.R")
fm_inc <- read_csv("../Data/farmincome_wealthstatisticsdata_march2019.csv") %>%
  filter(State == "US", 
         str_detect(VariableDescriptionTotal, "Net cash income$"),
         Year >= 1950) %>%
  rename(gdp_df = ChainType_GDP_Deflator) %>%
  mutate(Income = Amount/gdp_df) %>%
  mutate(year = as.Date(as.character(Year), format = "%Y"))
```

```{r, echo=FALSE}
fm_inc <- filter(fm_inc, Year >= 2010)

ggplot() +
  geom_line(data = fm_inc, aes(x=year, y=Income, group = 1), color = "black")
```

Cash receipts for corn, cotton, rice grain sorghum and wheat are all expecting increased receipts in 2019 compared to 2018. Among crop commodities the, the USDA forecasts corn to have the highest increase in cash receipts with cotton seeing the second highest percentage increase. Soybeans are predicted to have a reduction in receipts with sugar cane forecasts remaining stable.

Growth is expected for both animal products and crops. Crop receipts are projected to grow by 2.0% and animal product receipts are expected to grow by 2.6%. Figure 2 shows that the primary drivers of livestock growth are cattle products and dairy.

```{r, echo=FALSE}
p <- ggplot(income, aes(x = VariableDescriptionPart1, y = Amount)) +
  geom_bar(
    aes(color = year, fill = year),
    stat = "identity", position = position_dodge(0.8),
    width = 0.7
  ) +
  scale_fill_brewer(palette="Blues") +
  scale_colour_brewer(palette="Blues") +
  theme(axis.title.x=element_blank()) +
  labs(y = "US Dollars") +
  theme(legend.position="bottom")

p
```

```{r, echo=FALSE}
p <- ggplot(receipts, aes(x = VariableDescriptionPart1, y = Amount)) +
  geom_bar(
    aes(color = year, fill = year),
    stat = "identity", position = position_dodge(0.8),
    width = 0.7
  ) +
  scale_fill_brewer(palette="Blues") +
  scale_colour_brewer(palette="Blues") +
  theme(axis.title.x=element_blank()) +
  labs(y = "US Dollars") +
  theme(legend.position="bottom")

p 
```

### Implications for Louisiana
Figure 4 shows the composition of receipts in Louisiana in 2017 and 2010. Crop commodities have increased in importance in Louisiana since 2010. Soybeans have grown as a proportion of the Louisiana farm economy more so than any other crop. Among animal products, poultry revenues tend to dominate the revenue picture. As the USDA is projecting relatively stable outcomes for poulrty this year, growth in the Louisiana farm economy will largely depend on the performance of key crop commodities. The USDA projects growth for most of the major USDA crop commodities. The primary drivers that the USDA forecasts that encourages this change is growth in price of many commodities. Soybeans is predicted to buck the growth trend of the other commodities. However, growth in other commodities, such as corn, cotton and to some extent, rice, appear poised to offset the difference. 

```{r, echo=FALSE}
  pie = ggplot(LA_rcpts[[1]], aes(x="", y=Amount, fill=VariableDescriptionPart1)) + geom_bar(stat="identity", width=1)
  
  # Convert to pie (polar coordinates) and add labels
  pie = pie + coord_polar("y", start=0) + geom_text(aes(label = paste0(prop, "%")), position = position_stack(vjust = 0.5), color = "white")
  
  # Add color scale (hex colors)
  pie = pie + scale_fill_manual(values=c("#55DDE0", "#33658A", "#2F4858", "#F6AE2D", "#F26419", "#999999", 	"#008B8B", "#0000CD", "#A52A2A")) 
  
  # Remove labels and add title
  pie = pie + labs(x = NULL, y = NULL, fill = NULL, title = str_c("Louisiana Cash Receipts Composition in", " 2010"))
  
  # Tidy up the theme
  pie + theme_classic() + theme(axis.line = element_blank(),
                                axis.text = element_blank(),
                                axis.ticks = element_blank(),
                                plot.title = element_text(hjust = 0.5, color = "#666666"))
  
  
  pie = ggplot(LA_rcpts[[2]], aes(x="", y=Amount, fill=VariableDescriptionPart1)) + geom_bar(stat="identity", width=1)
  
  # Convert to pie (polar coordinates) and add labels
  pie = pie + coord_polar("y", start=0) + geom_text(aes(label = paste0(prop, "%")), position = position_stack(vjust = 0.5), color = "white")
  
  # Add color scale (hex colors)
  pie = pie + scale_fill_manual(values=c("#55DDE0", "#33658A", "#2F4858", "#F6AE2D", "#F26419", "#999999", 	"#008B8B", "#0000CD", "#A52A2A")) 
  
  # Remove labels and add title
  pie = pie + labs(x = NULL, y = NULL, fill = NULL, title = str_c("Louisiana Cash Receipts Composition in", " 2017"))
  
  # Tidy up the theme
  pie + theme_classic() + theme(axis.line = element_blank(),
                                axis.text = element_blank(),
                                axis.ticks = element_blank(),
                                plot.title = element_text(hjust = 0.5, color = "#666666"))
```

### Expenses
Interest rates, labor, total. 

